Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-26 qhtv2.tex
fixes on optimal solution

\begin{theorem}
	For $M \geq w (2\log_2(w) + \log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
\end{theorem}

@@

	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long). Thus a requirement of $w (2\log_2(w) + \log_2(|\Gamma|))$ bits for this DDF to work.

	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element was present in the sliding window.
\end{proof}
The dependence on $\log_2 |\Gamma|$ can be droped, at the cost of allowing 
errors:
\begin{theorem}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.

@@

When $\log_2|\Gamma| > 2 \log_2 w$ (which is the case of most practical use cases) this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory.

>>>>

\begin{theorem}
	For $M \geq w (\log_2(w) + 2\log_2(|\Gamma|))$, the sliding window DDP can be solved exactly (with no errors) in constant time.
\end{theorem}

@@

	The size of the queue is $w\log_2 |\Gamma|$, the size of the dictionary is $w (\log_2 |\Gamma| + \log_2 w)$ (as the dictionary cannot have more than $w$ keys at the same time, a dictionary key occupies $\log_2 |\Gamma|$ bits and a counter cannot go over $w$, thus being less than $\log_2 w$ bits long). Thus a requirement of $w (\log_2(w) + 2\log_2(|\Gamma|))$ bits for this DDF to work.

	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact account of how many times each element was present in the sliding window.
\end{proof}
The dependence on $\log_2 |\Gamma|$ can be dropped, at the cost of allowing 
errors:
\begin{theorem}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.

@@

When $\log_2|\Gamma| > 5 \log_2 w$ this DDF outperforms the naïve strategy\footnote{The naïve strategy consisting of storing the $w$ elements of the sliding window, requiring $w \log_2|\Gamma|$ bits of memory.}, both in terms of time and memory, at the cost of a minimal error. When $\log_2|\Gamma| > 2 \log_2 w$, it outperforms the exact solution described sooner in terms of memory.
